Eurovision Song Contest: semifinal 1, 2009

### 2022-07-14 inst/eurovision.Rmd
fixes #146

```{r}
preference
```
Now, take the first column of `preference`.  This represents the order
of preferences of Montenegro (`ME`).  Their favourite was [last row]
Bosnia & Herzegovina (`BA`), who they gave rank 1 to (that is, 12
points).  Their second favourite was Macedonia (`MK`), their third was
Turkey (`TR`), and so on.  They were not allowed to vote for themselves,
which is why the first row is `NA`.  So the order was: `BA` (first),
`MK` (second) , `TR` (third), `IS` (fourth), `RO` (fifth), `IL`
(sixth), `AM` (seventh), `FI` (eigthth), `BY` (ninth), `MT` (tenth).
The other countries (`CZ`, `BE`, `SW`, `CH`, `BG`, `PT`) came joint
last and did not receive any points from Montenegro.  Note the final
two rows corresponding to votes cast by Germany and the UK, who did
not compete and therefore cast votes for all competitors.

@@

```{r,label=loadeurohyper2,cache=TRUE}
a <- read.table("euro_ranks.txt",header=TRUE)
jj <- table(a$country)
wanted_countries <- names(jj[jj >= 10])
a <- a[a$country %in% wanted_countries,]
H <- hyper2()
for(y in unique(a$year)){
   H <- H + race((a$country)[a$year == y])
}
H
```

@@

Now use `hyper3` and follow `RB_BB_LF()` in
`plackett_luce_monster.Rmd`

>>>>

```{r,printpref}
preference
```
Now, take the first column of `preference`.  This represents the order
of preferences of Montenegro (`ME`).  Their favourite was [last row]
Bosnia & Herzegovina (`BA`), who they gave rank 1 to (that is, 12
points).  Their second favourite was Macedonia (`MK`), their third was
Turkey (`TR`), and so on.  They were not allowed to vote for themselves,
which is why the first row is `NA`.  So the order was: `BA` (first),
`MK` (second) , `TR` (third), `IS` (fourth), `RO` (fifth), `IL`
(sixth), `AM` (seventh), `FI` (eigthth), `BY` (ninth), `MT` (tenth).
The other countries (`CZ`, `BE`, `SW`, `CH`, `BG`, `PT`) came joint
last and did not receive any points from Montenegro.  Note the final
two rows corresponding to votes cast by Germany and the UK, who did
not compete and therefore cast votes for all competitors.

@@

```{r,label=loadeurohyper2,cache=TRUE}
a <- read.table("euro_ranks.txt",header=TRUE)
jj <- table(a$country)
wanted_countries <- names(jj[jj >= 10])
a <- a[a$country %in% wanted_countries,]
H <- hyper2()
for(y in unique(a$year)){
   H <- H + race((a$country)[a$year == y])
}
summary(H)
```

@@

Now use `hyper3` and follow `RB_BB_LF()` in
`plackett_luce_monster.Rmd`.  The blocs follow those of Price 2020.

```{r,plm}
scandinavia <- c("Denmark","Finland","Iceland","Norway","Sweden")

balkans  <- c("Italy","Serbia","Albania","BosHerz") # red
eastern  <- c("Russia","Ukraine","Moldova","Armenia","Azerbaijan", "Malta","Israel") # purple
black    <- c("Hungary","Romania","Greece","Cyprus") # orange
iberia   <- c("Spain","Germany") # blue
northern <- c("Denmark", "Estonia", "Finland", "France", "Iceland", "Lithuania", "Netherlands", "Norway", "Sweden", "UK") # green

l <- list(balkans=balkans,eastern=eastern,black=black,iberia=iberia,northern=northern)

ab <- c(balkans,eastern,black,iberia,northern)
stopifnot(all(ab %in% wanted_countries))
stopifnot(all(wanted_countries %in% ab))

list2ec <- function(l){
  jj <- stack(setNames(l,seq_along(l)))
  out <- as.integer(c(jj$ind))
  names(out) <- jj$values
  return(out)
}

print(a$year)

bloc <- function(lam){
  out <- hyper3()
  e <- list2ec(l)
  for(y in unique(a$year)){
     v <- a$country[a$year==y]
     ec <- e[names(e) %in% v]
     out <- out + cheering3(v=v, e=ec,h=rep(lam,length(unique(e))))
   } 
  return(out)
}

Ha <- bloc(1.888)
Hb <- bloc(1.9)
```

Now maximize it:

```{r,maxbloc,cache=TRUE}
maxp(Ha,n=2,give=TRUE)
maxp(Hb,n=2,give=TRUE)
```

```{r,maxhelp,cache=TRUE}
o <- function(lam){
   H <- bloc(lam)
   return(maxp(Hb,give=TRUE,n=1)$likes)
}

o(1)
o(2)

lam <- seq(from=0.6,to=1.5,len=4)
```

# References {-}

A. Price 2020. "Identifying voting blocs in the Eurovision Song Contest".  Towards Data Science,
`https://medium.com/towards-data-science/identifying-voting-blocs-in-the-eurovision-song-contest-4792065fc337`
